\begin{acknowledgementslong}
This thesis would not have been possible without the many amazing people that I have had the good fortune of meeting in my life. I would first like to thank my supervisor Prof. Robertus Erd\'elyi for his time, guidance and for allowing me to undertake this PhD. I would like to thank Mr Findlay for his excellent maths teaching at Leith Academy, and Prof. James McLaughlin for supervising my B.Sc. thesis at Northumbria University, first igniting my interest in solar physics.

To all my friends in H23 (Farhad, Rahul, No\'emi, Rachael, Tam\'as, Norby and Freddie), I want to thank you for our numerous conversations science and non-science related. I have particularly enjoyed our dungeon and dragons group (Ellie, Drew, Hope, Mihai and Ben), which has kept me sane and entertained during the process of this PhD. My fellow PhD cohort Matt, I could not have asked for a better person to share the whole experience of starting and finishing a PhD with. You have increased my knowledge of solar physics and made me think about many philosophical issues that have changed my worldview. I will miss the interesting conversations only being a desk away.

I am grateful to my parents and brothers (Coinneach, Eoghann and Tim), no words can truly express how important you have all been in my life, and for getting me to this point. I want to thank my partner Lauren for sticking by me throughout my PhD, you have been nothing but caring and supportive and I would not have been able to complete this without you. I know moving from Edinburgh to live in Sheffield has been difficult for you at times, but I have enjoyed living with you in the same place after 4 years of a long distance relationship. I have enjoyed exploring a new location with you and I hope we get to explore many more places together. I love you very much.

Finally, I would like to thank my Grandpa Ewan MacKenzie who passed away 2 weeks before his 90th birthday in December 2018. I remember our many conversations growing up about religion, the origins of the universe, and at what point would a single drop of water cause a dam to burst. I do not doubt that these conversations stoked my interest in science and a desire to try and gain some understanding of the complexities that occur in nature. 
%I think the strange circumstances that COVID has created has highlighted how important expressing one's gratitude to one another while we can not be limited to the tradition of a thesis.
\end{acknowledgementslong}