%------------------------------------------------------------------------------
\chapter{Conclusion and Future Work}
\label{chap:con_and_fut_work}
%-------------------------------
\section{Conclusion}
\label{sec:con}
%-------------------------------
The thesis aimed to investigate the fundamental dynamics and morphology of spicular jets. We have achieved this through a simple model, which uses a momentum pulse to drive the jets to simulate a transfer of mass in an idealised solar atmosphere and with a vertical uniform magnetic field. We have taken full advantage of MPI-AMRVAC mesh options to simulate the synthetic jets rising and falling dynamics with a high spatial resolution. In Chapter~\ref{chap:sj} vertical of the jet launching was investigated. An extensive parameter space was investigated, that determined spicule dynamics and morphology are sensitive to the parameter related to the driver (lifetimes and initial amplitude) and magnetic environment (magnetic field strength). The vertical and horizontal evolution of spicules is measured with our own automated jet tracking software. By using the jet tracking software we capture the main observable features of spicules with the synthetic jets, as we obtained similar heights, speeds, widths and trajectories. Despite numerous numerical studies, there have been few that have reported on the CSW variations and fine structures of spicular jets. We report on both of these and find complex fine structures in the jet beam of spicules due to shock waves, which also create symmetrical deformation of the jet boundary. These fine structures are yet to be observed, but we show that higher resolution observations with telescopes such as DKIST may be able to identify these fine structures.  \np
%
In Chapter~\ref{chap:tilted_jets} we continued to study with the same model for launching jets but explored the effects of misalignment between the direction of the driver and the magnetic field have on the dynamics and morphology of the synthetic jet. The tilt of the synthetic jet flows introduces interesting dynamics that were not seen in Chapter~\ref{chap:sj}. The main result of this study even with small tilts angles of $5\%$ there is a significant impact on the appearance of the synthetic jets. In this thesis, we have presented one of the few models that obtained both the transverse and horizontal dynamics of the spicule. An interesting result is the misaligned flows cause whip motions and redistribution of the densities to the jet edges. We tentatively put forward that the whip motions is possible a consequence of a DKI, but further research is required. Our research highlights the importance of properly tracking the central axis of the jets to obtain accurate jet trajectories and CSWs measurements. Non-filed aligned flows give another possibility for producing transverse motion in spicules. Given the complexity of the structure of the atmosphere that spicules propagate in, I think it's likely that non-field flow will occur, and it's an important aspect to include in any models of spicules. \np
%
Chapter~\ref{cap:obs} we revisit the straight jets and compare their properties with H$\alpha$ observations captured by SST. CSW variations are present in both observations and synthetic jets. By assuming that these waves are caused by standing waves, we perform a wavelet analysis to measure any significant wave periods. One of the main results in this thesis is that we are the first to report differences in the jet boundary deformation when the jet is in its rising or falling phase. Under the wave interpretation, there is frequency modulation in the falling phase of all the jets, with shorter periods in the falling phase in comparison to the rising phase. We propose this due to the change in direction of the mass flows of the jet with respect to the waves. In this wave-based framework, the results of the synthetic jets could be interpreted as identifying the fundamental mode and its 1st overtone of the sausage wave. However, I think that the results for the CSW variations of the synthetic jets highlight that we should be cautious with this interpretation. As described in Chapter~\ref{chap:tilted_jets}, we showed that CSW variations are possible due to supersonic flows which can be responsible for CSW variations. The boundary deformation of the synthetic jets shows no obvious sign of having an antinode, which may indicate CSW variation are not due to waves, but rather a consequence of the supersonic flow. This result should be kept in mind for observers reporting variations of spicule widths, as there may be other phenomena that can account for these motions. \np
%
The numerical study presented here has limitations when compared against the spicules actual nature. To have a closer match with spicules, extra physics would need to be included, such as radiate transfer, heat conduction, and deploying a 3D model. These limitations are mostly addressed in the future work section. Despite this, there is value in studying less complex models as it gives insight into the fundamental nature of spicules and allows us to more easily unpick the phenomena occurring in the simulations. I think this thesis highlights the importance of identifying what is driving the jets, as it is the most important factor for determining their dynamics and morphology. We are at the beginning of the next generation of solar telescopes with mirror sizes approximately four times that of SST, such as DKIST  which recently released the highest resolution image of the Sun's surface to date and allowed us to see features as small as $30~\rm{km}$, and EST with first light planned in $2026$. When this data becomes available, hopefully, we can advance our knowledge of the fine structuring of the spicules and pin down their driving mechanism. This would be a significant step forward and allow us to narrow down the appropriate numerical models from which to simulate spicules. 
%-------------------------------
\section{Future Work}
\label{sect:fut_work}
%-------------------------------
Multiple improvements can be undertaken to build upon the existing work in this thesis. The jet tracking code for the tilted examples could be improved further. Its current weakness is that it relies on horizontal slits to track the central axis. It would be better if one autonomously separated the left and right boundary of the jet, which is not a trivial task. Then for each boundary, measure a set distance to assign data points to match up with its boundary counterpart. Then by taking the midpoints of these pairs would yield a more accurate position of the central jet axis. Steps that need to be undertaken to blur lines between numerical simulation and observations are as follows. Spicules are 3D objects, therefore with a 2D model we may be missing import dynamics, for example, torsional motions \citep{dePontieu2012ApJ752L12D}, and in astrophysical jets it is possible for RTI to form at the boundary in 3D simulations jet for fast moving jets \citep{Matsumoto772L1M}. A 3D simulation would better capture the dynamical motion of the spicules and may yield interesting results for the behaviour of the boundary deformation. All the simulations in this thesis use a simplified solar atmosphere, it would be more appropriate to base the atmospheric stratification on semi-empirical data such as VALC or C7 atmospheric model \citep{Vernazza1981ApJS45635V,Avrett2008ApJS175229A}. More complex physics could be added, radiate transfer and heat conduction are important to include as they can impact the final height of the spicules \citep{Sterling1990ApJ349647S}. These additional physics are key if we wish to study the synthetic jets contribution to chromospheric/coronal heating. Carrying out a two fluid model of the simulation could be another avenue to investigate, as neutral could play an important role in spicule evolution \citep{kuzma2017ApJ84978K}. Another direction to investigate would be to try different magnetic field configurations, I think it would be very interesting to see how an expanding flux tube would impact the presence of the knots. One major improvement of the model, particularly useful for comparing to observations, would be to use forward modelling to convert the parameter of the simulation into observables. For example the FoMo code \citep{Doorsselaere2016FrASS34V}, is set up to accept MPI-AMRVAC data structures. Forward modelling would allow for a more concrete comparison to observations and may allow us to pick out potential observational signatures for the jet phenomena simulated throughout the thesis.